---
title: "Virasak SOKUN"
output: 
  html_document:
    toc: True
    toc_float: True
    
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br> 

### Hello:

<br>

Welcome to my page. My name is **Virasak SOKUN**, a business analyst graduate. I created this website to show you a little bit about myself, my passion, and my work that I have done so far within the line of my career path. You can find out more about my background and experience on [My Resume](Resume.html) page. 

Feel free to drop by and chat! ;) 

*Note*: All of the visualisations display on this website are just examples. 

<br>

### What I am passionate about?
<br>

I am passionate about data and automation. I believe advancing digital technology and improve data insights exploration are the two important components that would lead organisation to achieve sustainable operation and competitive advantages. 

<br>

### Examples of my technical skills and work

<br>

This is just a simple map I built for fun using data from my old uni's assignments and skills I self-learned. You can reach out to me if you want to learn that.

<br>

```{r libraries, echo = FALSE, message = FALSE}
library("tidyverse")
library("sf")
library("leaflet")
library("readxl")
library("plotly")
```

```{r download necessary shapefile, echo = FALSE, message = FALSE}
download.file(
  url = "http://www.naturalearthdata.com/http//www.naturalearthdata.com/download/50m/cultural/ne_50m_admin_0_countries.zip",
  destfile = "data/world-shape-files.zip")

unzip("data/world-shape-files.zip", 
      exdir = "data/world-shape-files")
```

```{r echo = FALSE, message = FALSE}
world_shapefiles <- read_sf(dsn = "data/world-shape-files/")

data_world <- read_excel("data/sony-dataset.xlsx", sheet = "Survey Data")
```

```{r Data Wrangling, echo = FALSE, message = FALSE}
data_world <- data_world %>%
  mutate_if(is.factor, as.character) %>%
  select(Country, Adverts, Sales, Airplay, Gender,
         StreamingServices, Piracy, Age, `iTunes Download`,
         Genre, `Year Released`, Language) %>%
  rename(NAME = Country)


data_world_combined <- world_shapefiles %>%
  left_join(data_world)

```

```{r echo = FALSE, message=FALSE, out.width="100%"}
est_numeric_palette <- colorNumeric("Blues", domain = data_world_combined$Sales)

data_world_combined %>%
  group_by(NAME) %>%
  summarise(Sales = mean(Sales)) %>%
  leaflet() %>%
  addPolygons(weight = 1,
              label = ~NAME,
              popup = ~paste("Country", NAME, "<br/>", Sales),
              fillColor = ~est_numeric_palette(Sales),
              fillOpacity = 0.8,
              color = "#000") %>% 
  addLegend(pal = est_numeric_palette,
            value = ~Sales) %>%
  setView(0,0, zoom = 1)

```
<br>
### Simple Stacked Bar Chart
<br>
```{r bar chart, echo = FALSE, message = FALSE, warning = FALSE, out.width="100%"}

data_world_combined %>% 
  group_by(NAME, Genre) %>%
  summarise(Sales = mean(Sales)) %>%
  plot_ly() %>%
  add_trace(x = ~Sales,
            y = ~NAME,
            color = ~Genre,
            type = "bar")%>%
  layout(barmode = "stack",
         margin = list(l = 200))
```

<br>

### Some of my achievements

<br> 

I was a member of the top 10 finalists of the "Global Analytics Competition 2019" as organized by the University of Maryland, Maryland, USA. The competition theme was about exploring insights of the environmental issues in the world and suggesting data-driven solutions. The competition process involved collecting data from available governmental data sources, cleaning, collating, and generating insights with recommended solutions around environmental issues. The process involved collecting data from available sources and government websites, cleaning, collating, analysing, and generating insights as well as recommended solutions. 
<br>

You can access the video I made for the competition here ;)

<br>

<iframe width="560" height="315" src="https://www.youtube.com/embed/hIu_OGpoHg0?rel=0" frameborder="0" allowfullscreen></iframe>

<br>

For more information about the competition, you can visit through this website: https://na.eventscloud.com/ehome/372646/799034/ 





